### 2021-04-09 Chapter-4/Chapter-4.tex
Updates from Overleaf

\subsection{Model Leakages}
\section{Approximate Model Counting}
\label{MCreasons}
In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and showed how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas. Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$). However, preliminary experiments showed that this approach was far too expensive to use with real-world applications. In this section, we discuss the bottlenecks in this approach and propose a practical solution.

@@

According to the Definition~\ref{def}, to calculate the amount of leaked
information, the key is to calculate the cardinality
of $K^o$. Suppose an attacker can observe $n$ leakage sites, and each leakage
site has the following constraints: $c_{\addr{1}}, c_{\addr{2}}, \ldots,
    c_{\addr{n}}$ respectively. The total leakage can be calculated from the constraint
$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}}) = c_{\addr{1}} \land c_{\addr{2}}
    \land \ldots \land c_{\addr{n}}$.
The problem of estimating the total leaked
information can be reduced to the problem of counting the number of different
solutions that satisfies the constraint
$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$.
A simple method is to pick elements $k$ from $K$ and check if an
element is also contained in $K^o$. Assume $q$ elements satisfy this condition. In
expectation, we can use $\frac{k}{q}$ to approximate the value of
$\frac{|K|}{|K^o|}$.

@@

Since we use $L = \log_{2}p$ to estimate the amount of leaked information, we
can have the following error propagation formula $\Delta L = \frac{\Delta
        p}{p\ln2}$ by taking the derivative from Definition~\ref{def}. For \tool, we want the error of estimated leaked
information ($\Delta L$) to be less than 1 bit. So we get $\frac{\Delta
        p}{p\ln2} \leq 1$. Therefore, as long as $ n \geq \frac{1.96^2(1-p)}{p(\ln2)^2}$, we have
95\% confidence that the error of estimated leaked information is less than 1 bit.
During the simulation, if $n$ and $p$ satisfy this inequality, the Monte Carlo
simulation will terminate.

@@

\tool\ reports that there are control-flow and data access types of leakages
in the non-bit-slicing implementation (line 6 and line 7 in Figure~\ref{fig:SBOX_da}). The number of leaked bits is
5.0 and 4.4, respectively. At line 6, according to Definition~\ref{def}, the
input set $K$ is $[0,2^8-1]$, the observed input set $K^o$ is $[0,2^3-1]$. Thus,
the leakage $L_{\beta(k)\rightarrow o}$ based on the observation ($o$) is
$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|} = 8-3 = 5$ bit, which
confirms the result from \tool. Similarly, we can verify the result of the other
leakage site. \tool{} reports no leakage on the bit-slicing implementation.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{def}, it means the leakage is very severe.

>>>>

\section{Approximate Model Counting}
\label{MCreasons}
In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and showed how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas. Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$). However, preliminary experiments showed that this approach was far too expensive to use with real-world applications. In this section, we discuss the bottlenecks in this approach and propose a practical solution.

@@

According to the Definition~\ref{chapter4:def}, to calculate the amount of leaked
information, the key is to calculate the cardinality
of $K^o$. Suppose an attacker can observe $n$ leakage sites, and each leakage
site has the following constraints: $c_{\addr{1}}, c_{\addr{2}}, \ldots,
    c_{\addr{n}}$ respectively. The total leakage can be calculated from the constraint
$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}}) = c_{\addr{1}} \land c_{\addr{2}}
    \land \ldots \land c_{\addr{n}}$.
The problem of estimating the total leaked
information can be reduced to the problem of counting the number of different
solutions that satisfies the constraint
$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$.
A simple method is to pick elements $k$ from $K$ and check if an
element is also contained in $K^o$. Assume $q$ elements satisfy this condition. In
expectation, we can use $\frac{k}{q}$ to approximate the value of
$\frac{|K|}{|K^o|}$.

@@

Since we use $L = \log_{2}p$ to estimate the amount of leaked information, we
can have the following error propagation formula $\Delta L = \frac{\Delta
        p}{p\ln2}$ by taking the derivative from Definition~\ref{chapter4:def}. For \tool, we want the error of estimated leaked
information ($\Delta L$) to be less than 1 bit. So we get $\frac{\Delta
        p}{p\ln2} \leq 1$. Therefore, as long as $ n \geq \frac{1.96^2(1-p)}{p(\ln2)^2}$, we have
95\% confidence that the error of estimated leaked information is less than 1 bit.
During the simulation, if $n$ and $p$ satisfy this inequality, the Monte Carlo
simulation will terminate.

@@

\tool\ reports that there are control-flow and data access types of leakages
in the non-bit-slicing implementation (line 6 and line 7 in Figure~\ref{fig:SBOX_da}). The number of leaked bits is
5.0 and 4.4, respectively. At line 6, according to Definition~\ref{chapter4:def}, the
input set $K$ is $[0,2^8-1]$, the observed input set $K^o$ is $[0,2^3-1]$. Thus,
the leakage $L_{\beta(k)\rightarrow o}$ based on the observation ($o$) is
$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|} = 8-3 = 5$ bit, which
confirms the result from \tool. Similarly, we can verify the result of the other
leakage site. \tool{} reports no leakage on the bit-slicing implementation.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe.

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{equation} \label{eq:2}
  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
\end{equation}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              &   &   &   &   & A &                 \\
        5              &   &   &   &   &   & A &             \\
        6              &   &   &   &   &   &   & A           \\
        7              &   &   &   &   &   &   &   & A       \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A Serious Leakage}\label{fig:example1}
\end{figure}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              & A &   &   &   &   &                 \\
        5              &   & A &   &   &   &   &             \\
        6              &   &   & A &   &   &   &             \\
        7              &   &   &   & A &   &   &   &         \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A Minor Leakage. }\label{fig:example2}
\end{figure}
On the other hand, the second example also have a side-channel leakages at line 7. However, the leakage is slightly different. Still, we test the program with input from $0, 1, \dots, 7$. However, we find the attacker can not uniquely determine the secret based on the observation of table $T$. For example. both $0$ and $4$ read the first the item of the table. Therefore, we think the vulnerability is slightly minor than the previous one. Here comes with the definition of the amount of leaked information of the vulnerability.

@@

With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{fig:example1} and Figure~\ref{fig:example2} respectively. In Figure~\ref{fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed. Therefore, the information leakage is $log_2{8} = 3$ bits. In Figure~\ref{fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed. Therefore, the information leakage is $log_2{4} = 2$ bits. We test the program with $8$ inputs. Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$. According to Equation~\ref{chapter5:eq1}. the secret-dependent data accesses in Figure~\ref{fig:example1} can leak the sensitive information totally.

@@

Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{fig:example1} and Figure~\ref{fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.

@@

\subsection{Overview}
Figure~\ref{fig:workflow} shows an overview of our side-channel leakages quantification tool. Given the source code of the victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program. To assist the illustration, we divide the workflow of ~\ctool{} into three steps. For the first step, we build the target program from the source code. After that, we give them random inputs to the victim program and run the target program and record each of the address in the binary file is hit or not and store the information in a bitmap. Next, we analyze the side-channel leakage from the address access bitmap. We split the address space into several segments to speed up the comparison according to Meta information. Finally, \ctool{} Generate the final leakage report. For each leakage sites, \ctool{} gives the conservative estimation of the information leakage. Every leakage site in the report is a true leakage and there is no false positives.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
  \caption{The workflow of \ctool{}. We try to divide the \ctool{} into three steps to assist the illustration. }\label{fig:workflow}
\end{figure}

@@

\subsubsection{Estimate The Leaked Information}
According to Definition~\ref{def}, we quantify the information leakage based on the distribution of the observation. If we calculate the information leakage from an $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$. While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.

@@

\begin{sidewaystable}
\footnotesize
\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{table:over_result}
\begin{tabular}{lrrrrrrrrrrrr}\toprule

>>>>

\begin{equation} \label{chapter:eq:5}
  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
\end{equation}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              &   &   &   &   & A &                 \\
        5              &   &   &   &   &   & A &             \\
        6              &   &   &   &   &   &   & A           \\
        7              &   &   &   &   &   &   &   & A       \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A Serious Leakage}\label{chapter5:fig:example1}
\end{figure}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              & A &   &   &   &   &                 \\
        5              &   & A &   &   &   &   &             \\
        6              &   &   & A &   &   &   &             \\
        7              &   &   &   & A &   &   &   &         \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A Minor Leakage. }\label{chapter5:fig:example2}
\end{figure}
On the other hand, the second example also have a side-channel leakages at line 7. However, the leakage is slightly different. Still, we test the program with input from $0, 1, \dots, 7$. However, we find the attacker can not uniquely determine the secret based on the observation of table $T$. For example. both $0$ and $4$ read the first the item of the table. Therefore, we think the vulnerability is slightly minor than the previous one. Here comes with the definition of the amount of leaked information of the vulnerability.

@@

With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2} respectively. In Figure~\ref{chapter5:fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed. Therefore, the information leakage is $log_2{8} = 3$ bits. In Figure~\ref{chapter5:fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed. Therefore, the information leakage is $log_2{4} = 2$ bits. We test the program with $8$ inputs. Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$. According to Equation~\ref{chapter5:eq1}. the secret-dependent data accesses in Figure~\ref{chapter5:fig:example1} can leak the sensitive information totally.

@@

Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{chapter5:fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{chapter5:fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{chapter5:fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.

@@

\subsection{Overview}
Figure~\ref{chapter5:fig:workflow} shows an overview of our side-channel leakages quantification tool. Given the source code of the victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program. To assist the illustration, we divide the workflow of ~\ctool{} into three steps. For the first step, we build the target program from the source code. After that, we give them random inputs to the victim program and run the target program and record each of the address in the binary file is hit or not and store the information in a bitmap. Next, we analyze the side-channel leakage from the address access bitmap. We split the address space into several segments to speed up the comparison according to Meta information. Finally, \ctool{} Generate the final leakage report. For each leakage sites, \ctool{} gives the conservative estimation of the information leakage. Every leakage site in the report is a true leakage and there is no false positives.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
  \caption{The workflow of \ctool{}. We try to divide the \ctool{} into three steps to assist the illustration. }\label{chapter5:fig:workflow}
\end{figure}

@@

\subsubsection{Estimate The Leaked Information}
According to Definition~\ref{chapter5:def}, we quantify the information leakage based on the distribution of the observation. If we calculate the information leakage from an $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$. While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.

@@

\begin{sidewaystable}
\footnotesize
\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{chapter5:table:over_result}
\begin{tabular}{lrrrrrrrrrrrr}\toprule
